---
title: "Isms PHiR 2015 Evaluation"
author: "mgutilla"
date: "Saturday, October 10, 2015"
output: html_document
---
This is a summary of evaluation data from a Public Health in the Rockies, held in Vail, Colorado September 16-18, 2015 

---------------------------------------------------------------------------
# Session: *"Having Conversations about Isms"*.

**Presenters: Molly Gutilla, Erin McKay, Suzuho Shimasaki, and Kory Thomas**

## Write-in Responses

### What was the most valuable thing you learned in this session?
* How to have conversations about isms
* Steps to take for having these conversations
* Great conversations and new approaches to address difficult topics/issues
* First listen
* The skill of how to address or begin a conversation
* I enjoyed that timeline exercise and staring about assumptions. I found the conversations around gender identity fascinating
* The discussions, the honesty
* Thank you! This was a helpful start
* How to address uncomfortable situations at work and in my personal life
* Triggers and how to start the conversation
* Role playing
* I liked the difficult planning conversations planning worksheet
* Techniques and examples to start tough conversations
* Always good to take allotted time to think about these topics
* That not listening or taking action = participating in oppression
* Recognizing and addressing isms

### How could the session be improved?
* Would be great for a "201" version of changing our practices/programs to begin addressing isms
* More time to role play - less time on intro to isms
* More strategies for finding the space and opportunities to have these conversations
* I would have like to learn a few key phrases for the first line of the conversation - I think that's the hardest parting - knowing how to start
* Offer it to CDPHE
* More group discussion, a little less history
* More time
* Longer. What do you do when you hear implicit bias emerge from an ethnic group you aren't a part of? Isn't that condescending?
* It was great!
* Some concrete examples of how to start a conversation that is tough
* Provide handouts w/concrete examples of conversation starters. Also examples of how to re-center yourself. Missed opportunity to provide concrete skill building skills.
* Maybe a video example of a tactful conversation in practice


### Additional comments/observations
* Consider diving deeper by having these conversations that have impact at different levels of the social ecology
* Great job!
* Would have enjoyed more time!! Love this session - best of my day.
* Great Job!
* This was awesome! I loved it
* One of the most valuable presentations I've been at
* It would be cool, with all your expertise, to see/do a session on gender vs. sexuality and that topic in public health/health equity context. I would help.
* Great! Thanks!
* Excellent job!



```{r load,}
# load libraries, set working directory
library(ggplot2)
setwd("C:/Users/Molly/Documents/2_Papers/Conferences/PHiR_2015/Evaluation/PHiR_2015_evaluation")
getwd()

# read in data
isms <- read.csv('Isms_eval.csv')

# create objects for mean of each item to use in plots
meana <- mean(isms$a)
meanb <- mean(isms$b)
meanc <- mean(isms$c)
meand <- mean(isms$d)
meand2 <- mean(isms$d2)
meane <- mean(isms$e)
meane2 <- mean(isms$e2)
meanf <- mean(isms$f)
meang <- mean(isms$g)
meanh <- mean(isms$h)
meani <- mean(isms$i)

```

### Distribution of scale questions
#### where: 5 = strongly agree, 1= strongly disagree; mean shown as red dashed line

```{r create plots}

ggplot(isms, aes(x=a)) +
  geom_bar(alpha = 0.5, binwidth=1)  + 
  scale_x_discrete() +
  scale_y_continuous(limits=c(0,20)) +
   labs(title ="Statement: I am better able to identify isms in our society", x = "Score", y = "Count") +
  geom_vline(aes(xintercept=meana), colour="#BB0000", linetype="dashed", labels="Mean", show_guide=TRUE) 

ggplot(isms, aes(x=b)) +
  geom_bar(alpha = 0.5, binwidth=1)  + 
  scale_x_discrete() +
  scale_y_continuous(limits=c(0,20)) +
   labs(title ="Statement: I have a better understanding of how isms function 
        in our society", x = "Score", y = "Count") +
  geom_vline(aes(xintercept=meanb), colour="#BB0000", linetype="dashed", labels="Mean", show_guide=TRUE) 

ggplot(isms, aes(x=c)) +
  geom_bar(alpha = 0.5, binwidth=1)  + 
  scale_x_discrete() +
  scale_y_continuous(limits=c(0,20)) +
   labs(title ="Statement: I am able to briefly describe the historical impact of racism, sexism
        heterosexism, and ableism on health", x = "Score", y = "Count") +
  geom_vline(aes(xintercept=meanc), colour="#BB0000", linetype="dashed", labels="Mean", show_guide=TRUE) 

ggplot(isms, aes(x=d)) +
  geom_bar(alpha = 0.5, binwidth=1)  + 
  scale_x_discrete() +
  scale_y_continuous(limits=c(0,20)) +
   labs(title ="Statement: I have increased my comfort level in having conversations about
        isms", x = "Score", y = "Count") +
  geom_vline(aes(xintercept=meand), colour="#BB0000", linetype="dashed", labels="Mean", show_guide=TRUE) 

ggplot(isms, aes(x=e)) +
  geom_bar(alpha = 0.5, binwidth=1)  + 
  scale_x_discrete() +
  scale_y_continuous(limits=c(0,20)) +
   labs(title ="Statement: I have increased my skills in addressing isms", x = "Score", y = "Count") +
  geom_vline(aes(xintercept=meane), colour="#BB0000", linetype="dashed", labels="Mean", show_guide=TRUE) 

ggplot(isms, aes(x=d2)) +
  geom_bar(alpha = 0.5, binwidth=1)  + 
  scale_x_discrete() +
  scale_y_continuous(limits=c(0,20)) +
   labs(title ="Statement: Presenters were organized/had a clear presentation", x = "Score", y = "Count") +
  geom_vline(aes(xintercept=meand2), colour="#BB0000", linetype="dashed", labels="Mean", show_guide=TRUE) 

ggplot(isms, aes(x=e2)) +
  geom_bar(alpha = 0.5, binwidth=1)  + 
  scale_x_discrete() +
  scale_y_continuous(limits=c(0,20)) +
   labs(title ="Statement: Presenters provided useful information", x = "Score", y = "Count") +
  geom_vline(aes(xintercept=meane2), colour="#BB0000", linetype="dashed", labels="Mean", show_guide=TRUE) 

ggplot(isms, aes(x=f)) +
  geom_bar(alpha = 0.5, binwidth=1)  + 
  scale_x_discrete() +
  scale_y_continuous(limits=c(0,22)) +
   labs(title ="Statement: Presenter/participant interaction was appropriate", x = "Score", y = "Count") +
  geom_vline(aes(xintercept=meanf), colour="#BB0000", linetype="dashed", labels="Mean", show_guide=TRUE) 

ggplot(isms, aes(x=g)) +
  geom_bar(alpha = 0.5, binwidth=1)  + 
  scale_x_discrete() +
  scale_y_continuous(limits=c(0,20)) +
   labs(title ="Statement: Presenters used audio/visual aids well", x = "Score", y = "Count") +
  geom_vline(aes(xintercept=meang), colour="#BB0000", linetype="dashed", labels="Mean", show_guide=TRUE) 

ggplot(isms, aes(x=h)) +
  geom_bar(alpha = 0.5, binwidth=1)  + 
  scale_x_discrete() +
  scale_y_continuous(limits=c(0,20)) +
   labs(title ="Statement: Presenters allotted time well", x = "Score", y = "Count") +
  geom_vline(aes(xintercept=meanh), colour="#BB0000", linetype="dashed", labels="Mean", show_guide=TRUE) 

ggplot(isms, aes(x=i)) +
  geom_bar(alpha = 0.5, binwidth=1)  + 
  scale_x_discrete() +
  scale_y_continuous(limits=c(0,20)) +
   labs(title ="Statement: The session was timely in terms of current public health 
        practice", x = "Score", y = "Count") +
  geom_vline(aes(xintercept=meani), colour="#BB0000", linetype="dashed", labels="Mean", show_guide=TRUE) 

```
