---
title: "Intersectionalism PHiR 2015 Evaluation"
author: "mgutilla"
date: "Monday, September 28, 2015"
output: word_document
---
This is a summary of evaluation data from a Public Health in the Rockies, held in Vail, Colorado September 16-18, 2015 
session: *"Intersectionalism: How multiple identities influence health"*.

**The presenters were:
Molly Gutilla

**

## Write-in Responses

### What was the most valuable thing you learned in this session?

* The history/background of intersectionality and how it plays out in public health
* Watch our assumptions, esp. around data
* Very interesting concept and application to practice
* I think the most valuable thing I learned was how the different levels of education effects different races
* I learned about "ableism", never thought of myself as advantaged, only though of disabled people as "disadvantaged"
* Complexity of intersectionalities
* It's easy to make assumptions and these can be barriers to healthcare. Education is important.
* Terms, talking through difficult topics
* To look at the whole person and that it isn't all on the surface
* The definitions of intersectionalities. Still a very new term
* Intersectionality
* About the nature of the how disparities might be caused by structures in society
* Check assumptions, both my own and my clients
* Made me more aware of assumptions and how they impact and how we interact with people
* That we should pay attention to an individual and we shouldn't make assumptions
* Everything

### How could the session be improved?
*	I just wish I saw the beginning! Conflicting session! Actually, I just thought of something: A lot of the examples seems specific to direct service care. Maybe consider policy examples in the future since that is a powerful way to impact pop. Health and intersectionality of identities needs to be considered when creating/promoting PH policy
* Excellent
* Better connection of intersectionalities to everyday activites/work in public health
* It was great!
* Shorten it some
* Less time
* Make sure a few people don't dominate the conversation
* Get under our skin a bit
* Show videos

### Additional comments/observations
* This was wonderful! Thank you
* I learned a lot. Thank you
* Great job!
* This was a new model for me and helpful
* I wish there were clearer answers but there are only more questions
* Good use of research
* Need handouts for this session because you have GREAT INFO!!


```{r load,}
# load libraries, set working directory
library(ggplot2)
library(RColorBrewer)
setwd('C:/Users/Molly/Documents/2_Papers/Conferences/PHiR 2015/Evaluation')
getwd()

# read in data
inter <- read.csv('Isms_eval.csv')

# view summary statsitics for each item
summary(inter)


```

### Distribution of scale questions:

```{r create plots}

ggplot(inter, aes(x=a)) +
  geom_bar(alpha = 0.5, binwidth=1)  + 
  scale_x_discrete() +
  scale_y_continuous(limits=c(0,15)) +
   labs(title ="Question asked:", x = "Score", y = "Count") +
  geom_vline(aes(xintercept=4.25), colour="#BB0000", linetype="dashed", labels="Mean", show_guide=TRUE) 

ggplot(inter, aes(x=b)) +
  geom_bar(alpha = 0.5, binwidth=1)  + 
  scale_x_discrete() +
  scale_y_continuous(limits=c(0,15)) +
   labs(title ="Question asked:", x = "Score", y = "Count") +
  geom_vline(aes(xintercept=4.292), colour="#BB0000", linetype="dashed", labels="Mean", show_guide=TRUE) 

```

